Road Segment Prioritization for Bicycle Infrastructure

### 2021-03-06 README.Rmd
Remove quote markes from extended quote

> "Inadequate cycling infrastructure discourages cycling and wastes
> public money. Much cycling infrastructure in this country is
> inadequate. It reflects a belief, conscious or otherwise, that hardly
> anyone cycles, that cycling is unimportant and that cycles must take
> no meaningful space from more important road users, such as motor
> vehicles and pedestrians - [@departmentgearchange2020]"

>>>>

> Inadequate cycling infrastructure discourages cycling and wastes
 public money. Much cycling infrastructure in this country is
 inadequate. It reflects a belief, conscious or otherwise, that hardly
 anyone cycles, that cycling is unimportant and that cycles must take
 no meaningful space from more important road users, such as motor
 vehicles and pedestrians [@departmentgearchange2020]
